---
title: "ReportSourcing2"
author: "C.S.Lee"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        
params:
    pubDate: !r Sys.Date()
    DFSource: NA
---

```{r setup, include=FALSE}
Sys.setlocale( "LC_ALL", "Korean_Korea.949")
knitr::opts_chunk$set(echo=FALSE)

library(tidyverse)
library(lubridate)
library(htmltools)
#library(ggplot2)
#library(dplyr)
library(reshape2)
library(DT)

DFSource <- DFSource

theme_update(axis.title=element_text(size=20))
theme_update(axis.text=element_text(size=15))

```

Inputs {.sidebar}
=============================================

Summary Table  
 - [ContVarTable] page  
 - [CatVarTable] page  
 
Box Plot  
 - [cut] page  
 - [color] page 
 
Scatter Plot  
 - [price_carat] page  
 
 

 

ContVarTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`
No. of Observation : `r NROW(DFSource)`
No. of variables : `r NCOL(DFSource)`

Row {data-height=485}
---------------------------------------------

### 
```{r, contVarTable1}
summary <- function(x) {
  funs <- c(min, mean, max, sd)
  lapply(funs, function(f) f(x, na.rm=TRUE))
}

dfContVar <- Filter(is.numeric, DFSource)
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame
# dfTableContVar <- as.data.frame(lapply(lapply(dfContVar, summary), unlist))

# row.names(dfTableContVar) <- c("최소", "평균", "최대", "편차")
DT::datatable(dfTableContVar,
              rownames = c("min", "mean", "max", "sd")) %>%
  formatRound(c("carat","depth","table","price","x","y","z"),
              c(2,1,0,0,2,2,2)) 


```

Row {data-height=485}
---------------------------------------------
### 
```{r, contVarTable2}
summary <- function(x) {
  funs <- c(NROW(x))
}
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame

DT::datatable(dfTableContVar)
```


CatVarTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`

Row {data-height=170}
---------------------------------------------

### 
```{r, catVarTable1}
# dfCatVar <- Filter(is.factor, DFSource)
catVarNames <- c("cut", "color", "clarity")
dfCatVar <- DFSource[,catVarNames]
dfCatVarLevels <- list("cut", "color", "clarity")
names(dfCatVarLevels) <- catVarNames
for(i in 1:NROW(catVarNames)) {
  if(is.factor(DFSource[,catVarNames[i]][[1]])) {
    dfCatVarLevels[[catVarNames[i]]] <-
      attr(diamonds[,catVarNames[i]][[1]], "levels")
  } else {
    dfCatVarLevels[[catVarNames[i]]] <-
      as.character(unique(DFSource[,catVarNames[i]]))
  }
}

dfTableCatVar <-dfCatVarLevels %>% lapply(str_c,collapse=", ") %>%
  as.data.frame 
DT::datatable(dfTableCatVar, options=list(dom='t'))
```

Row {data-height=800}
---------------------------------------------
### 
```{r, catVarTable2}
renderTable <- function(dfGroups) {
  calcMean <- function(index, varName) {
    valueVec <- dfContVar[index,varName]
    mean(valueVec, na.rm=TRUE)
  }
  noRecord <- lapply(dfGroups$.rows, NROW) %>% unlist
  price <- lapply(dfGroups$.rows, calcMean, varName="price") %>% unlist
  carat <- lapply(dfGroups$.rows, calcMean, varName="carat") %>% unlist
  x <- lapply(dfGroups$.rows, calcMean, varName="x") %>% unlist
  y <- lapply(dfGroups$.rows, calcMean, varName="y") %>% unlist
  dfTable <- dfGroups %>% mutate(noRecord=noRecord, price=price, carat=carat, x=x, y=y) %>% 
    select(-.rows)  
  DT::datatable(dfTable, rownames=FALSE, 
                options=list(dom='t')) %>%
    formatRound(c("price", "carat", "x", "y"), c(0,2,2,2))
                # options=list(dom='t', autoWidth=TRUE, columnDefs=list(list(width='200px'))))
  
}
dfGroups <- DFSource %>% group_by(cut) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

### 
```{r, catVarTable3}
dfGroups <- DFSource %>% group_by(color) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

### 
```{r, catVarTable4}
dfGroups <- DFSource %>% group_by(clarity) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

cut{data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, cut_boxplot1}
 ggplot(data=DFSource, mapping=aes(x=cut, y=price)) + geom_boxplot(mapping=aes(group=cut))
```

### 
```{r, cut_boxplot2}
 ggplot(data=DFSource, mapping=aes(x=cut, y=carat)) + geom_boxplot(mapping=aes(group=cut))
```

Row {data-height=500}
---------------------------------------------

### 
```{r, cut_boxplot3}
 ggplot(data=DFSource, mapping=aes(x=cut, y=x)) + geom_boxplot(mapping=aes(group=cut))
```

### 
```{r, cut_boxplot4}
 ggplot(data=DFSource, mapping=aes(x=cut, y=y)) + geom_boxplot(mapping=aes(group=cut))
```

color{data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, color_boxplot1}
 ggplot(data=DFSource, mapping=aes(x=color, y=price)) + geom_boxplot(mapping=aes(group=color))
```

### 
```{r, color_boxplot2}
 ggplot(data=DFSource, mapping=aes(x=color, y=carat)) + geom_boxplot(mapping=aes(group=color))
```

Row {data-height=500}
---------------------------------------------

### 
```{r, color_boxplot3}
 ggplot(data=DFSource, mapping=aes(x=color, y=x)) + geom_boxplot(mapping=aes(group=color))
```

### 
```{r, color_boxplot4}
 ggplot(data=DFSource, mapping=aes(x=color, y=y)) + geom_boxplot(mapping=aes(group=color))
```

price_carat {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, price_carat_1}
renderScatterPlot <- function(x,y,z) {
  paramsVec <- c(x,y,z)
  dfGraph <- DFSource[,paramsVec]
  # dfGraph[,color] <- as.factor(dfGraph[,color])
  ggplot(dfGraph, aes_string(x=x, y=y, color=z)) + geom_point() 
}
#renderScatterPlot(x="carat", y="price", z="cut")
```

### 
```{r, price_carat_2}
#renderScatterPlot(x="carat", y="price", z="color")
```

Row {data-height=500}
---------------------------------------------

### 
```{r, price_carat_3}
#renderScatterPlot(x="carat", y="price", z="clarity")
```

### 
```{r, price_carat_4}
# renderScatterPlot(x="disp", y="mpg", color="carb")
```

