---
title: "ReportSourcing2"
author: "C.S.Lee"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        
params:
    pubDate: !r Sys.Date()
    DFSource: NA
    MaxDomainExplore: NA
    MinDomainExplore: NA
---

```{r setup, include=FALSE}
Sys.setlocale( "LC_ALL", "Korean_Korea.949")
knitr::opts_chunk$set(echo=FALSE)

# library(tidyverse)
# library(lubridate)
# library(htmltools)
#library(ggplot2)
#library(dplyr)
# library(reshape2)
# library(DT)

DFSource <- params$DFSource
MaxDomainExplore <- params$MaxDomainExplore
MinDomainExplore <- params$MinDomainExplore

theme_update(axis.title=element_text(size=20))
theme_update(axis.text=element_text(size=15))

```

Inputs {.sidebar}
=============================================

Summary Table  
 - [ContVarTable] page  
 - [CatMeanTable] page  
 
CatMean Table  
 - [CatFailTable1] page   
 - [CatFailTable3] page  
 - [CatFailTable5] page  
 
  
 
 
 

 

ContVarTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`
No. of Observation : `r NROW(DFSource)`
No. of variables : `r NCOL(DFSource)`

Row {data-height=485}
---------------------------------------------

### 
```{r, contVarTable1}
summary <- function(x) {
  funs <- c(min, mean, max, sd)
  lapply(funs, function(f) f(x, na.rm=TRUE))
}

dfContVar <- Filter(is.numeric, DFSource)
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame
# dfTableContVar <- as.data.frame(lapply(lapply(dfContVar, summary), unlist))

# row.names(dfTableContVar) <- c("최소", "평균", "최대", "편차")
DT::datatable(dfTableContVar,
              rownames = c("min", "mean", "max", "sd"),
              colnames = c("displacement"="disp", "horsepower"="hp")) %>%
  formatRound(c("mpg","cyl","displacement","horsepower","drat","wt","qsec","vs","am","gear","carb"),
              c(1,0,1,0,2,3,2,0,0,0,0)) 


```

Row {data-height=485}
---------------------------------------------
### 
```{r, contVarTable2}
summary <- function(x) {
  funs <- c(NROW(x))
}
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame

DT::datatable(dfTableContVar)
```


CatMeanTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`

Row {data-height=170}
---------------------------------------------

### 
```{r, catVarTable1}
# dfCatVar <- Filter(is.factor, DFSource)
dfCatVar <- DFSource[,c("cyl", "vs", "am","gear", "carb")]
catVarNames <- c("cyl", "vs", "am","gear", "carb")
dfCatVarLevels <- list("cyl", "vs", "am","gear", "carb" )
names(dfCatVarLevels) <- catVarNames
for(i in 1:NROW(catVarNames)) {
  if(is.factor(DFSource[,catVarNames[i]][[1]])) {
    dfCatVarLevels[[catVarNames[i]]] <-
      attr(diamonds[,catVarNames[i]][[1]], "levels")
  } else {
    dfCatVarLevels[[catVarNames[i]]] <-
      as.character(unique(DFSource[,catVarNames[i]]))
  }
}

dfTableCatVar <- lapply(dfCatVarLevels,sort) %>% lapply(str_c,collapse=", ") %>%
  as.data.frame 
DT::datatable(dfTableCatVar, options=list(dom='t'))
```

Row {data-height=250}
---------------------------------------------
### 
```{r, catVarTable2}
renderTable <- function(dfGroups) {

  calcMean <- function(index, varName) {
    valueVec <- dfContVar[index,varName]
    mean(valueVec, na.rm=TRUE)
  }
  noRecord <- lapply(dfGroups$.rows, NROW) %>% unlist
  mpg <- lapply(dfGroups$.rows, calcMean, varName="mpg") %>% unlist
  disp <- lapply(dfGroups$.rows, calcMean, varName="disp") %>% unlist
  hp <- lapply(dfGroups$.rows, calcMean, varName="hp") %>% unlist
  wt <- lapply(dfGroups$.rows, calcMean, varName="wt") %>% unlist
  dfTable <- dfGroups %>% mutate(noRecord=noRecord, mpg=mpg, disp=disp, hp=hp, wt=wt) %>% 
    select(-.rows)  
  DT::datatable(dfTable, rownames=FALSE, 
                options=list(dom='t')) %>%
    formatRound(c("mpg", "disp", "hp", "wt"), c(1,1,0,3))
                # options=list(dom='t', autoWidth=TRUE, columnDefs=list(list(width='200px'))))
  
}
dfGroups <- dfContVar %>% group_by(cyl) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

Row {data-height=250}
---------------------------------------------

### 
```{r, catVarTable3}
dfGroups <- dfContVar %>% group_by(am) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

### 
```{r, catVarTable4}
dfGroups <- dfContVar %>% group_by(vs) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

Row {data-height=300}
---------------------------------------------

### 
```{r, catVarTable5}
dfGroups <- dfContVar %>% group_by(am, vs) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

CatFailTable1{data-navmenu="CatFail Table"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable1}
### 수동 개발용 코드 ###
### 수동 개발용 코드 ###
# DFSource <- curSampleExplore                ###  sampling 리포트인 경우 curSampleExplore가 DFSource임
# dfContVar <- Filter(is.numeric, DFSource)   ###
# MinDomainExplore <- c(20,NA,NA,200,2)
# names(MinDomainExplore) <- c("mpg","cyl","disp","hp","wt")
# MaxDomainExplore <- c(30,NA,NA,NA,4)
# names(MaxDomainExplore) <- c("mpg","cyl","disp","hp","wt")
### 수동 개발용 코드 ###
### 수동 개발용 코드 ###
OBTVarList <- list(sliceVar=NA, boundVar=NA)
varName1 <- extractCatVarName(DFSource)
varName2 <- extractNumVarName(DFSource)
func1 <- function(x) {
  length(unique(DFSource[,x])) < 4
}
bool <- vapply(varName2, func1, FUN.VALUE = logical(1))
sliceVarSet <- union(varName1, varName2[bool])
sliceVarBase <- c("am")
sliceVarSet <- setdiff(sliceVarSet, sliceVarBase)
OBTVarList[["boundVar"]] <- c(varName2[!bool])
noSliceVar <- length(sliceVarBase) + 1

renderDFGroups <- function(x) {
  OBTVarList[["sliceVar"]] <<- c(sliceVarBase, sliceVarSet[x] )
  switch(as.character(noSliceVar),
         "1" = {
           dfGroups <- DFSource %>% group_by(get(OBTVarList[["sliceVar"]][1]))
         },
         "2" = {
           
           dfGroups <- DFSource %>% group_by(get(OBTVarList[["sliceVar"]][1]), get(OBTVarList[["sliceVar"]][2]))
  
         },
         "3" = {
  
         },
         "4" = {
  
         })
  return(dfGroups)
}

dfGroups <- renderDFGroups(1)


# dfGroups <- DFSource %>% group_by(get(OBTVarList[["sliceVar"]][1]), get(OBTVarList[["sliceVar"]][2]))
renderTable2 <- function(dfGroups) {
  dfGroupsAttr <- dfGroups %>% attr("groups")
  colnames(dfGroupsAttr) <- c(OBTVarList[["sliceVar"]], ".rows")
  OBTable <- dfGroupsAttr %>% select(-.rows)  
  
  calcFailPercent <- function(df) {
    # df <- dfGroups                         ### 수동 개발용 코드 ###
    if(is.null(attr(df,"group"))){
        bool <- df$bHOT == "Normal"
        mean(bool)
    } else {
        ratio <- vector("double", nrow(attr(df,"group")))
        for(i in 1:nrow(attr(df,"group"))) {
            slice <- df[attr(df, "group")[[i,".rows"]], ]
            bool <- slice$bHOT == "Normal"
            ratio[i] <- mean(bool)
        }
        ratio
    }
  }
  countOBL <- function(index, df, varName, bound) {
    # browser()
    valueVec <- df[index,varName]
    bool <- valueVec < bound
    sum(bool)
  }
  countOBU <- function(index, df, varName, bound) {
    # browser()
    valueVec <- df[index,varName]
    bool <- valueVec > bound
    sum(bool)
  }

  noRecord <- lapply(dfGroupsAttr$.rows, NROW) %>% unlist
  FailPercent <-  calcFailPercent(df=dfGroups) * 100
  OBTable <- OBTable %>%  mutate(noRecord=noRecord, FailPercent=FailPercent)
  listVector <- as.data.frame(dfGroupsAttr[,".rows"])[,".rows"]
  for(i in 1:length(OBTVarList[["boundVar"]])) {
    boundVar <- OBTVarList[["boundVar"]][i]
    minValue <- MinDomainExplore[boundVar]
    maxValue <- MaxDomainExplore[boundVar]
    # minValue <- 20
    # maxValue <- 20
    if(!is.na(minValue) || !is.na(maxValue)) {
      OBTable[paste0(boundVar,"_OBL")] <- 
        vapply(listVector, countOBL, df=dfGroups, varName=boundVar, bound=minValue,FUN.VALUE=numeric(1) )
      OBTable[paste0(boundVar,"_OBU")] <- 
        vapply(listVector, countOBU, df=dfGroups, varName=boundVar, bound=maxValue,FUN.VALUE=numeric(1) )
      
    }

      
  }


  DT::datatable(OBTable, rownames=FALSE, 
                options=list(dom='t')) 
  
}
renderTable2(dfGroups=dfGroups)

```

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable2}
dfGroups <- renderDFGroups(2)
renderTable2(dfGroups=dfGroups)

```

CatFailTable3{data-navmenu="CatFail Table"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable3}
dfGroups <- renderDFGroups(3)
renderTable2(dfGroups=dfGroups)

```

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable4}
dfGroups <- renderDFGroups(4)
renderTable2(dfGroups=dfGroups)

```

CatFailTable5{data-navmenu="CatFail Table"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable5}
dfGroups <- renderDFGroups(5)
renderTable2(dfGroups=dfGroups)

```

Row {data-height=500}
---------------------------------------------

### 
```{r, catFailTable6}
dfGroups <- renderDFGroups(6)
renderTable2(dfGroups=dfGroups)

```

test1{data-navmenu="Test"}
=============================================

### 
```{r, test1}
library(summarytools)
# DFSource <- curSampleExplore                ###  sampling 리포트인 경우 curSampleExplore가 DFSource임
# view(dfSummary(DFSource))
dfSummary(DFSource)

```