---
title: "ReportSourcing2"
author: "C.S.Lee"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        
params:
    pubDate: !r Sys.Date()
    DFSource: NA
---

```{r setup, include=FALSE}
Sys.setlocale( "LC_ALL", "Korean_Korea.949")
knitr::opts_chunk$set(echo=FALSE)

library(tidyverse)
library(lubridate)
library(htmltools)
#library(ggplot2)
#library(dplyr)
library(reshape2)
library(DT)

DFSource <- DFSource

theme_update(axis.title=element_text(size=20))
theme_update(axis.text=element_text(size=15))

```

Inputs {.sidebar}
=============================================

Summary Table  
 - [ContVarTable] page  
 - [CatVarTable] page  
 
Box Plot  
 - [cylinder] page  
  - [auto_manual] page  
 
Scatter Plot  
 - [mpg_disp] page  
 - [hp_disp] page   
 - [hp_mpg] page  
 
 
 

 

ContVarTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`
No. of Observation : `r NROW(DFSource)`
No. of variables : `r NCOL(DFSource)`

Row {data-height=485}
---------------------------------------------

### 
```{r, contVarTable1}
summary <- function(x) {
  funs <- c(min, mean, max, sd)
  lapply(funs, function(f) f(x, na.rm=TRUE))
}

dfContVar <- Filter(is.numeric, DFSource)
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame
# dfTableContVar <- as.data.frame(lapply(lapply(dfContVar, summary), unlist))

# row.names(dfTableContVar) <- c("최소", "평균", "최대", "편차")
DT::datatable(dfTableContVar,
              rownames = c("min", "mean", "max", "sd"),
              colnames = c("displacement"="disp", "horsepower"="hp")) %>%
  formatRound(c("mpg","cyl","displacement","horsepower","drat","wt","qsec","vs","am","gear","carb"),
              c(1,0,1,0,2,3,2,0,0,0,0)) 


```

Row {data-height=485}
---------------------------------------------
### 
```{r, contVarTable2}
summary <- function(x) {
  funs <- c(NROW(x))
}
dfTableContVar <- lapply(dfContVar, summary) %>% lapply(unlist) %>% as.data.frame

DT::datatable(dfTableContVar)
```


CatVarTable{data-navmenu="Summary Table"}
=============================================

Row {data-height=30}
---------------------------------------------
Publication Date : `r params$pubDate`

Row {data-height=170}
---------------------------------------------

### 
```{r, catVarTable1}
# dfCatVar <- Filter(is.factor, DFSource)
dfCatVar <- DFSource[,c("cyl", "vs", "am","gear", "carb")]
catVarNames <- c("cyl", "vs", "am","gear", "carb")
dfCatVarLevels <- list("cyl", "vs", "am","gear", "carb" )
names(dfCatVarLevels) <- catVarNames
for(i in 1:NROW(catVarNames)) {
  if(is.factor(DFSource[,catVarNames[i]][[1]])) {
    dfCatVarLevels[[catVarNames[i]]] <-
      attr(diamonds[,catVarNames[i]][[1]], "levels")
  } else {
    dfCatVarLevels[[catVarNames[i]]] <-
      as.character(unique(DFSource[,catVarNames[i]]))
  }
}

dfTableCatVar <- lapply(dfCatVarLevels,sort) %>% lapply(str_c,collapse=", ") %>%
  as.data.frame 
DT::datatable(dfTableCatVar, options=list(dom='t'))
```

Row {data-height=250}
---------------------------------------------
### 
```{r, catVarTable2}
renderTable <- function(dfGroups) {
  calcMean <- function(index, varName) {
    valueVec <- dfContVar[index,varName]
    mean(valueVec, na.rm=TRUE)
  }
  noRecord <- lapply(dfGroups$.rows, NROW) %>% unlist
  mpg <- lapply(dfGroups$.rows, calcMean, varName="mpg") %>% unlist
  disp <- lapply(dfGroups$.rows, calcMean, varName="disp") %>% unlist
  hp <- lapply(dfGroups$.rows, calcMean, varName="hp") %>% unlist
  wt <- lapply(dfGroups$.rows, calcMean, varName="wt") %>% unlist
  dfTable <- dfGroups %>% mutate(noRecord=noRecord, mpg=mpg, disp=disp, hp=hp, wt=wt) %>% 
    select(-.rows)  
  DT::datatable(dfTable, rownames=FALSE, 
                options=list(dom='t')) %>%
    formatRound(c("mpg", "disp", "hp", "wt"), c(1,1,0,3))
                # options=list(dom='t', autoWidth=TRUE, columnDefs=list(list(width='200px'))))
  
}
dfGroups <- dfContVar %>% group_by(cyl) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

Row {data-height=250}
---------------------------------------------

### 
```{r, catVarTable3}
dfGroups <- dfContVar %>% group_by(am) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

### 
```{r, catVarTable4}
dfGroups <- dfContVar %>% group_by(vs) %>% attr("groups")
renderTable(dfGroups=dfGroups)
```

Row {data-height=300}
---------------------------------------------



cylinder{data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, cyl_boxplot1}
 ggplot(data=DFSource, mapping=aes(x=cyl, y=mpg)) + geom_boxplot(mapping=aes(group=cyl))
```

### 
```{r, cyl_boxplot2}
 ggplot(data=DFSource, mapping=aes(x=cyl, y=disp)) + geom_boxplot(mapping=aes(group=cyl))
```

Row {data-height=500}
---------------------------------------------

### 
```{r, cyl_boxplot3}
 ggplot(data=DFSource, mapping=aes(x=cyl, y=hp)) + geom_boxplot(mapping=aes(group=cyl))
```

### 
```{r, cyl_boxplot4}
 ggplot(data=DFSource, mapping=aes(x=cyl, y=wt)) + geom_boxplot(mapping=aes(group=cyl))
```

auto_manual{data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, am_boxplot1}
 ggplot(data=DFSource, mapping=aes(x=am, y=mpg)) + geom_boxplot(mapping=aes(group=am))
```

### 
```{r, am_boxplot2}
 ggplot(data=DFSource, mapping=aes(x=am, y=disp)) + geom_boxplot(mapping=aes(group=am))
```

Row {data-height=500}
---------------------------------------------

### 
```{r, am_boxplot3}
 ggplot(data=DFSource, mapping=aes(x=am, y=hp)) + geom_boxplot(mapping=aes(group=am))
```

### 
```{r, am_boxplot4}
 ggplot(data=DFSource, mapping=aes(x=am, y=wt)) + geom_boxplot(mapping=aes(group=am))
```

mpg_disp {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, mpg_disp_1}
renderScatterPlot <- function(x, y, color) {
    dfGraph <- DFSource %>% select(x,y,color) 
    dfGraph[,color] <- as.factor(dfGraph[,color])
    ggplot(dfGraph, aes_string(x=x, y=y, color=color)) + geom_point() 
}
renderScatterPlot(x="disp", y="mpg", color="cyl")
```

### 
```{r, mpg_disp_2}
renderScatterPlot(x="disp", y="mpg", color="am")
```

Row {data-height=500}
---------------------------------------------

### 
```{r, mpg_disp_3}
renderScatterPlot(x="disp", y="mpg", color="gear")
```

### 
```{r, mpg_disp_4}
renderScatterPlot(x="disp", y="mpg", color="carb")
```

hp_disp {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, hp_disp_1}
renderScatterPlot(x="disp", y="hp", color="cyl")
```

### 
```{r, hp_disp_2}
renderScatterPlot(x="disp", y="hp", color="am")
```

Row {data-height=500}
---------------------------------------------

### 
```{r, hp_disp_3}
renderScatterPlot(x="disp", y="hp", color="gear")
```

### 
```{r, hp_disp_4}
renderScatterPlot(x="disp", y="hp", color="carb")
```

hp_mpg {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, hp_mpg_1}
renderScatterPlot(x="mpg", y="hp", color="cyl")
```

### 
```{r, hp_mpg_2}
renderScatterPlot(x="mpg", y="hp", color="am")
```

Row {data-height=500}
---------------------------------------------

### 
```{r, hp_mpg_3}
renderScatterPlot(x="mpg", y="hp", color="gear")
```

### 
```{r, hp_mpg_4}
renderScatterPlot(x="mpg", y="hp", color="carb")
```