---
title: "탐색 그래프 Report"
author: "C.S.Lee"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        
params:
    pubDate: !r Sys.Date()
    df: NA
    aesList: NA
---

```{r setup, include=FALSE}
Sys.setlocale( "LC_ALL", "Korean_Korea.949")
# Sys.setlocale( "LC_ALL", "C")
knitr::opts_chunk$set(echo=FALSE)

library(tidyverse)
library(lubridate)
library(htmltools)
#library(ggplot2)
#library(dplyr)
library(reshape2)
library(DT)
library(broom)
library(modelr)

df <- params$df
aesList <- params$aesList

theme_update(axis.title=element_text(size=20))
theme_update(axis.text=element_text(size=15))

extractNumVarName <- function(df) {
  # numeric variable 만 추출
  varNameVec <- colnames(df)
  func1 <- function(x) {
    is.numeric(df[,x])
  }
  booleanVec <- vapply(varNameVec, func1, FUN.VALUE=logical(1))
  # catVar <- varNameVec[!booleanVec]
  numVar <-  varNameVec[booleanVec]
  return(numVar)
}
extractCatVarName <- function(df) {
  # numeric variable 만 추출
  varNameVec <- colnames(df)
  func1 <- function(x) {
    is.numeric(df[,x])
  }
  booleanVec <- vapply(varNameVec, func1, FUN.VALUE=logical(1))
  catVar <- varNameVec[!booleanVec]
}
 # df <- dfReportCommon
aesList[["x"]] <- setdiff(extractNumVarName(df), 
                          c(aesList[["y"]], aesList[["size"]], aesList[["shape"]]))
dfX <- df[,aesList[["x"]]]
# x <- df[,"wt"]
y <- df[,aesList[["y"]]]
calcR2 <- function(x) {
  df2 <- data.frame(x=x,y=y)
  x2 <- x * x
  modelResult <- lm(y~x + x2, data=df2)
  # adjR2 <- broom::glance(modelResult)[["adj.r.squared"]] # 음수값이 나오는 경우 발생
  R2 <- broom::glance(modelResult)[["r.squared"]]
}
R2Vec <- vapply(dfX, calcR2, numeric(1))
meltR <- melt(R2Vec)
orderR <- order(meltR$value, decreasing=TRUE)
aesList[["x"]] <- row.names(meltR)[orderR]
# browser()
```

Inputs {.sidebar}
=============================================


Scatter Plot  
 - [Scatter1] page  
 - [Scatter2] page   
 - [Scatter3] page  
 
Box Plot  
  - [Box1] page  
  - [Box2] page  
  - [Box3] page  
  
 
 
 

 


Scatter1 {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter_1}
# df <- DFSource
renderScatterPlot <- function(x, y, color=NULL, size=NULL, shape=NULL) {
  # x="wt"; y="mpg"; color="cyl"
    dfGraph <- df[,c(x,y,color, size, shape)] 
    dfGraph[,size] <- as.factor(dfGraph[,size])
    dfGraph[,shape] <- as.factor(dfGraph[,shape])
    if(!is.null(color) && !is.factor(dfGraph[,color])  && length(unique(dfGraph[,color])) < 6 && x!=color) {
      dfGraph[,color] <- as.factor(dfGraph[,color])
    }
    dfModel <- dfGraph[,c(x, y)]
    colnames(dfModel) <- c("xVec", "yVec")
    dfModel <- dfModel %>% mutate(xVec2 = xVec * xVec)
    model <- lm(yVec ~ xVec + xVec2,data=dfModel)
    # dfPred <- add_predictions(dfModel, model)
    myfunc <- function(x) {
      model[["coefficients"]][1] + model[["coefficients"]][2] * x + model[["coefficients"]][3]*x*x
    }
    labelAnnotate <- paste0("R2 : ", round(R2Vec[x],3))
    xAnnotate = min(dfGraph[,x],na.rm=TRUE) +
                       0.15*(max(dfGraph[,x],na.rm=TRUE)-min(dfGraph[,x],na.rm=TRUE))
    ggplot(dfGraph) + geom_point(aes_string(x=x, y=y, color=color, size=size, shape=shape)) +
      # geom_line(data=dfPred, aes(x=xVec, y=pred, color=NULL)) 
      stat_function(fun=myfunc, geom="line", color="black") +
      annotate("text",
               x=xAnnotate, y=min(dfGraph[,y]), label=labelAnnotate, color="black", size=2)
    
}
# renderScatterPlot(x="wt", y="mpg", color="cyl")
if(!is.na(x=aesList[["x"]][1]))
  renderScatterPlot(x=aesList[["x"]][1], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, scatter_2}
if(!is.na(x=aesList[["x"]][2]))
  renderScatterPlot(x=aesList[["x"]][2], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter_3}
if(!is.na(x=aesList[["x"]][3]))
  renderScatterPlot(x=aesList[["x"]][3], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, scatter_4}
if(!is.na(x=aesList[["x"]][4]))
  renderScatterPlot(x=aesList[["x"]][4], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Scatter2 {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter_5}
if(!is.na(x=aesList[["x"]][5]))
  renderScatterPlot(x=aesList[["x"]][5], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, sactter_6}
if(!is.na(x=aesList[["x"]][6]))
  renderScatterPlot(x=aesList[["x"]][6], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter_7}
if(!is.na(x=aesList[["x"]][7]))
  renderScatterPlot(x=aesList[["x"]][7], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, scatter_8}
if(!is.na(x=aesList[["x"]][8]))
  renderScatterPlot(x=aesList[["x"]][8], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Scatter3 {data-navmenu="Scatter Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter9}
if(!is.na(x=aesList[["x"]][9]))
  renderScatterPlot(x=aesList[["x"]][9], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, scatter10}
if(!is.na(x=aesList[["x"]][10]))
  renderScatterPlot(x=aesList[["x"]][10], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Row {data-height=500}
---------------------------------------------

### 
```{r, scatter11}
if(!is.na(x=aesList[["x"]][11]))
  renderScatterPlot(x=aesList[["x"]][11], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

### 
```{r, scatter12}
if(!is.na(x=aesList[["x"]][12]))
  renderScatterPlot(x=aesList[["x"]][12], y=aesList[["y"]], color=aesList[["color"]],
                    size=aesList[["size"]], shape=aesList[["shape"]])
```

Box1 {data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, box_1}
# df <- DFSource

constNames <- extractConstName(df)
varNames <- setdiff(colnames(df), constNames)
xVarNames <- union(constNames[1], varNames)
aesList[["x"]] <- setdiff(xVarNames, aesList[["y"]])

renderBoxPlot <- function(x, y) {
  # x="wt"; y="mpg"; color="cyl"
  dfGraph <- df[,c(x,y)] 

  if(is.factor(dfGraph[,x]) || length(unique(dfGraph[,x]))<10 )  {
      gg <- ggplot(dfGraph, aes_string(x=x, y=y)) + geom_boxplot(aes_string(group=x))
  } else {
      gg <- ggplot(dfGraph, aes_string(x=x, y=y)) + 
        # geom_boxplot(aes_string(group=cut_number(dfGraph[,x], 10)))
        geom_boxplot(aes_string(group=cut_interval(dfGraph[,x], 10)))
  }
  gg
}
# renderBoxPlot(x="sampleCode", y="mpg")
if(!is.na(x=aesList[["x"]][1]))
  renderBoxPlot(x=aesList[["x"]][1], y=aesList[["y"]] )
```

### 
```{r, box_2}
if(!is.na(x=aesList[["x"]][2]))
  renderBoxPlot(x=aesList[["x"]][2], y=aesList[["y"]] )
```

Row {data-height=500}
---------------------------------------------

### 
```{r, box_3}
if(!is.na(x=aesList[["x"]][3]))
  renderBoxPlot(x=aesList[["x"]][3], y=aesList[["y"]] )
```

### 
```{r, box_4}
if(!is.na(x=aesList[["x"]][4]))
  renderBoxPlot(x=aesList[["x"]][4], y=aesList[["y"]] )
```

Box2 {data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, box_5}
if(!is.na(x=aesList[["x"]][5]))
  renderBoxPlot(x=aesList[["x"]][5], y=aesList[["y"]] )
```

### 
```{r, box_6}
if(!is.na(x=aesList[["x"]][6]))
  renderBoxPlot(x=aesList[["x"]][6], y=aesList[["y"]] )
```

Row {data-height=500}
---------------------------------------------

### 
```{r, box_7}
if(!is.na(x=aesList[["x"]][7]))
  renderBoxPlot(x=aesList[["x"]][7], y=aesList[["y"]] )
```

### 
```{r, box_8}
if(!is.na(x=aesList[["x"]][8]))
  renderBoxPlot(x=aesList[["x"]][8], y=aesList[["y"]] )
```

Box3 {data-navmenu="Box Plot"}
=============================================

Row {data-height=500}
---------------------------------------------

### 
```{r, box_9}
if(!is.na(x=aesList[["x"]][9]))
  renderBoxPlot(x=aesList[["x"]][9], y=aesList[["y"]] )
```

### 
```{r, box_10}
if(!is.na(x=aesList[["x"]][10]))
  renderBoxPlot(x=aesList[["x"]][10], y=aesList[["y"]] )
```

Row {data-height=500}
---------------------------------------------

### 
```{r, box_11}
if(!is.na(x=aesList[["x"]][11]))
  renderBoxPlot(x=aesList[["x"]][11], y=aesList[["y"]] )
```

### 
```{r, box_12}
if(!is.na(x=aesList[["x"]][12]))
  renderBoxPlot(x=aesList[["x"]][12], y=aesList[["y"]] )
```